Security vs. Maintainability: \\ Fixing Vulnerabilities Obfuscates your Code

### 2019-01-28 paper/ICPC19/icpc19.tex
remove todo

\setcounter{lstannotation}{0}
\begin{lstlisting}[caption={Fix provided by OpenSSL developers to the CVE-2014-3506 vulnerability \Sof{@todo: Fix the regex issue}},label={lst:vuln}]
+ static unsigned long dtls1_max_handshake_message_len(const SSL *s){ /*!\annotation{lst:func1}!*/
+  unsigned long max_len = DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH;
+  if(max_len < (unsigned long)s->max_cert_list) /*!\annotation{lst:func2}!*/
+     return s->max_cert_list;
+  return max_len;
+ }

>>>>

\setcounter{lstannotation}{0}
\begin{lstlisting}[caption={Fix provided by OpenSSL developers to the
CVE-2014-3506 vulnerability},label={lst:vuln}]
+ static unsigned long dtls1_max_handshake_message_len(const SSL *s){ /*!\annotation{lst:func1}!*/
+  unsigned long max_len = DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH;
+  if(max_len < (unsigned long)s->max_cert_list) /*!\annotation{lst:func2}!*/
+     return s->max_cert_list;
+  return max_len;
+ }
